\documentclass{article}
%\usepackage[letterpaper]{geometry}
%\geometry{verbose,tmargin=25mm,bmargin=25mm,lmargin=20mm,rmargin=25mm,headheight=30mm,headsep=5mm,footskip=5mm}
\usepackage[dvips,papersize={8.5in,11in},tmargin=25mm,bmargin=25mm,headheight=15mm,headsep=5mm,lmargin=8mm,rmargin=25mm]{geometry}
\usepackage{fancyhdr}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{multicol}
\usepackage{longtable}
\pagestyle{fancy}

\setlength\parskip{\medskipamount}
\setlength\parindent{0pt}

% Este macro fue tomado de http://www.tug.org/pipermail/tugindia/2002-November/001018.html
% Para definir la última página


\hyphenation{pro-ble-ma imple-men-ta-ción na-tu-ral de-par-ta-men-to
  cons-truc-ti-vism linux}

\chead{{\Large \textbf {Curriculum Vitae}} \\
\textbf{Igor Támara Patiño}
}
\rhead{\thepage}
\lhead{}
\rfoot{}
\cfoot{ http://igor.tamarapatino.org/cv/ - igor@tamarapatino.org}
%\renewcommand{\headrulewidth}{0pt}

\begin{document}
\begin{longtable}{p{10cm}p{7cm}}
\noindent \textbf{Name}: José Igor Támara Patiño & \textbf{Last update}: 10/07/2007 \\
\textbf{Citizenship}: Colombian & \textbf{Sex}: Male \\
\textbf{Date of birth}: August 28, 1.976 &\textbf{Place of birth}: Bogotá, Colombia \\
\textbf{Status}: Father of a 2006 son &  \\
\textbf{Email}: igor@tamarapatino.org & \textbf{Identity document}: C.C. 79'627.373 Bogotá \\
\end{longtable}

This cv presents the studies I have done, my experiences on teaching
and habilities focused toward open unix flavored operating systems 
such as Linux and BSD.

If you want me to enhance some information in any aspect, please let
me know.
\section{Education}
{\center
\begin{longtable}{llc}
\hline
\textbf{Grade} & \textbf{Institution} & \textbf{Finished} \\
\hline
Systems Engineer & Universidad de los Andes (Bogotá) & 2000 \\
Mathematician & Universidad de los Andes (Bogotá) & 2000\\
\end{longtable}}

\noindent \textbf{Other}
{\center
\begin{longtable}{llc}
\hline
\textbf{Study} & \textbf{Institution} & \textbf{Time Period} \\
\hline
English(12 levels) & Centro Colombo-Americano (Bogotá) & 1991-1992 \\
Swimming(6 levels) & Colombian Red Cross (Bogotá) & 1990, 1993 \\
\end{longtable}}

\noindent \textbf{Languages}
{\center 
\begin{itemize}
\item Spanish : Mother tongue
\item Enlish : Written with sufficiency. mid level spoken
\item French : Able to read
\end{itemize}}

\section{Research and teaching}
\noindent \textbf{Research interests}
\begin{itemize}
\item Computer related : Natural Language Processing, Operating Systems,
  networks
\item Maths : Numerical Analysis
\item Teaching : Computer Assisted Instruction, Programming languages teaching
\end{itemize}

\subsection{Research experience}
{\center
\begin{longtable}{p{8.5cm}p{4.5cm}p{2.5cm}}
\hline
\textbf{Research} & \textbf{Team work} & \textbf{Time period} \\
\hline
Lab Director, bachelors projects director and assisting on
investigation lineaments & Sirio. Facultad Ingeniería
Fundación Universitaria San Martín. Rodrigo Moreno & 2001-2003 \\
Thesis: PLeNa. An approach to Natural language processing & Dra. Silvia Takahashi & 1999-2000 \\
Thesis: mathematical and numeric study of an elasticity problem &
Dr. Ahmed Ould Khaoua & 1998-2000 \\
\hline
\end{longtable}}


\subsection{Teaching Experience}
\begin{itemize}
\item At Pontificia Universidad Javeriana (Bogotá)\\
  \begin{longtable}{p{5cm}p{4cm}p{6cm}}
Course & Departament & Time Period \\
Programming Languages & Systems engineering & 2007-1 \\
Algorithm Analysis & Systems engineering & 2006-2 \\
\end{longtable}
\item At Fundación Universitaria San Martín (Bogotá) \\
  \begin{longtable}{p{5cm}p{4cm}p{6cm}}
Course & Department & Time period \\
Internet oriented programming & Systems engineering & 2002-2, 2003-1 \\
Basics of Object Oriented Programming & Systems engineering & 2001-2, 2002-1, 2003-1,
2003-2 \\
Functional and logic programming & Systems engineering & 2001-2, 2002-1, 2003-2 \\
Data Structures & Systems engineering & 2000-2 \\
Object Oriented Programming & Systems engineering & 2000-2 \\
  \end{longtable}
\item At Universidad de los Andes (Bogotá)\\
  \begin{longtable}{p{5cm}p{4cm}p{6cm}}
Course & Department & Time period \\
Integral Calculus & Maths & 1998-2,1999-1 \\
Differencial Calculus & Maths & 1998-1 \\
  \end{longtable}
\item At Gimnasio Fidel Cano School (Bogotá) \\
  \begin{longtable}{p{5cm}p{4cm}p{3cm}}
Course & Time period \\
Python  & 2004, 2006, 2007, 2008 \\
Python and Zope  & 2005 \\
Java & 2000-2003 \\
C and Java Programming & 1999 \\
Trigonometría &  1998 \\
  \end{longtable}
\end{itemize}

\subsection{Bachelor's projects director}
{\center
\begin{longtable}{p{8.2cm}p{3.8cm}p{1.5cm}p{3cm}}

\hline
\textbf{Subject} & \textbf{Author} & \textbf{Year} & \textbf{University}\\
\hline
WAP , XML and J2EE & Rodrigo Galvis & 2003 & FUSM \\
Java net games platform & Alexander Montealegre & 2003 & FUSM \\
Semiautomatic organization of repositories via web XML-Java & Sandra Romero & 2003 & FUSM \\
Study and use of the MONO platform (.NET on Linux) & Sandra Galeano &2003 & FUSM \\
Java code generator from UML & Yamil Rojas &2002 & FUSM \\
SMIL Editor & Nilo Atia &2002 & FUSM \\
PHP-WAP parking reservation system & Liliana Walteros &2002  & FUSM \\
web interface for IPtables & Edgar Mejía & 2001 & FUSM \\
\endhead
\multicolumn{2}{r}{Continues}
\endfoot
\endlastfoot
\end{longtable}
}

\subsection{Education related projects}
{\center
\begin{longtable}{p{6.8cm}p{4cm}p{3cm}p{2cm}}
\hline
\textbf{Project} & \textbf{Team work} & \textbf{Sponsor} &
\textbf{Time period} \\
\hline
SPT : Software for all. School students create software
& GFC & GFC & 2000- \\
Translation : School students making translations &
Various teachers & GFC & 2000- \\
Structio: colombian school model based on free software, free
documentation and constructivism & Voluntary group & Sourceforge & 1999- \\
PLeNa An approach to Natural Language Processing & Vladimir
Támara, Silvia Takahashi & Universidad de los Andes, GFC & 1999-2002 \\
training software and CAI for primary students & Jorge Támara, Vladimir Támara & GFC & 1987-1989 \\
\endhead
\multicolumn{2}{r}{Continues}
\endfoot
\endlastfoot
\hline
\end{longtable}
}
\section{Publications}
\begin{itemize}
\item Támara, Vladimir. Támara, José Igor. Guías para aprender a
  aprender linux en colegios. Structio Project. 2000-2003
\item Támara, José Igor. PLeNa: An approach to Natural Language
  Processing. Undergraduate Thesis. system engineering department. Universidad de los Andes. 2000.
\item Támara, José Igor.Mathematical and numerical study of an
  elasticity problem. Undergraduate Thesis. Maths department. Universidad de los Andes. 2000. 
\end{itemize}

\section{Computer related habilities}

I use Linux as operating system full tiem since 1999, I can work with
other unix flavored operating systems, my expertice on administration
includes X86, sparc and powerpc architectures, my base distribution is
Debian, in the past I have used RedHat and Suse.

\subsection{Developed software}
The software presented here is covered by GPL or is given to public
domain and can be donwloadable for free over the Internet, other
software products can be referenced as closed source and belong to
companies for whom I made them.

\begin{itemize}
\item GFPP : ``Flower Production Predictor''. Created and maintained a
  package used to predict the production of flowers for a
  farm. Developed in Java and tested on Linux and Windows. http://gfpp.sf.net
\item Gtypist : maintained for a short period a ``learning typing software''
\item gestiona : Software aimed to act as a white pages for school
  including students, workers and suppliers.  Part of the 
  Structio project http://structio.sf.net . Actually it's being
  developed, implemented in python and postgresql.
\item cuenta : At present, maintainer for this double entry account
  software that is subject to the colombian norms of accounting, and
  that shares the database with gestiona. Part of Structio  project
  http://structio.sf.net . It's on devel state. Implemented on
  PHP and postgresql.
\end{itemize}


\subsection{Programming languages}

Follows a programming languages listing that I've worked with. Noting
the programming language, the time working with it, and a self
evaluation expertise.
{\center
\begin{longtable}{p{2.2cm}p{10cm}p{2cm}p{1.5cm}}
\hline
\textbf{P. Language} & \textbf{Characteristics} & \textbf{Experience}
& \textbf{Level}\\
\hline
Python & My preferred language for education, I've oriented various
courses with it.  & 4 years & High\\
PHP & I've developed some web tools por Fundacion Universitaria San
Martín and for the Gimnasio Fidel Cano, I've oriented some
undergraduate courses with this language. & 4 years & High\\
Java & I developed GFPP in this language and used it for my
undegraduate project opting for my title as systems engineering. I've
also oriented some undergraduate courses as well as on school & 5 years & High\\
C & The first programming language used at the University, I've modified
some source code of free software to suit my needs. I also used
this in teaching on undergraduate and on GFC.& 7 years
 & Medium\\
Functional & Haskell and Caml teaching on undergraduate courses & 2
years & Medium\\
C\# & On Ikhnaie development, the next generation web interface for
Invytec working with silverlight & 3 months & Medium \\
Prolog & Teaching on undergraduate courses & 2 years & Medium \\
Perl & Just for learning & 1 year & Low \\
plpsql & plpythonu and procedural languages for Postgresql & 1 year &
High \\
Markup & I've created documentation with languages like \LaTeX,
DocBook, TeXInfo and SGML  XML and wiki dialects. & 5 years & High. \\
shell & shell programming in order to make my life easier on
administering a bunch of machines and server with hundred of users. & 4 years &
Medium \\
\hline
\end{longtable}
}

Aditionally I have worked with information that is on XML using tools
to transform it like XSLT and specific libraries of programming
languages such as Java and Python.

\subsubsection{Frameworks}
\label{sec:frame}

Among the habilities working with libraries I have worked with
frameworks for web development being Django the one I have more
experience with.   I have worked with Tryton a 
three-tiers high-level general purpose application platform over 
which ERPs can be built.

\subsubsection{Developing and Good Practices on Software}
\label{sec:good}

I work with distributed control version systems such as Mercurial or
Git and also with centralized version systems such as Subversion;
the development documentation and process of building software
is supplied by the use of wikis and many markup languages and
documentation systems such as Sphinx and the involvement on free
software and contents makes the heavy use of tools to gather and find
solutions in a collaborative with distributed teams.

\subsubsection{Translation processes}
\label{sec:trans}

Follows a list of project translations to Spanish where I have been
involved:
\begin{itemize}
\item Free Software Foundation : I helped on website translation.
\item Debian : I help on the translation and review on release notes
  and installation manual.
\item Mercurial : Cotranslation of the mercurial book.
\item Officeial Emacs Tutorial : Review and Quality Assurance of
  spanish translation of the Tutorial shipped with Emacs.
\item Moinmoin : Cotranslation of the help and overall moinmoin wiki
\item Tryton: Cotranslation of the server, client and modules of
  Tryton
\end{itemize}
\subsection{Systems administration}

Now some tools that I have work with as a system administrator.  The
main ability is planification, I have configured some LANs and
machines running linux.

{\center
\begin{longtable}{p{2.2cm}p{11.6cm}p{2.3cm}}
\hline
\textbf{Service} & \textbf{Explanation} & \textbf{Tools} \\
\hline
SMBD & Migration, creation and maintenance of information systems with
php, python, C, zope, wxwindows libraries.
& Postgresql, Sybase, Mysql \\
Email & Administration of email systems 7/24 with adittional protocols
like POP3, IMAP and mailing lists & exim, ssl, squirrelmail, mailman. \\
Web Servers & Configuration, administration y maintenance of web
servers, reverse proxies or for presenting dynamic content & apache,
zope \\
Wikis & setup, administration and extension via plugins for moinmoin
as wiki engine. \\
Dataless & dataless clusters administration, so the user info is
centralized as well as authentication & NIS / NFS \\
Users & Administration of machines that have more than one thousand of
users, where sometimes about 50 users where compiling, programming and
publishing info concurrently &  Shell, scripting, by hand configuration.\\
\hline
\end{longtable}
}


\section{Professional experience}
{\center
\begin{longtable}{p{5.4cm}p{2.1cm}p{9.5cm}}
\hline
\textbf{Place} & \textbf{Time period} & \textbf{Work} \\
\hline
Invytec & November 2008 To Date & Software Product Coordinator:
Help improve the infrastructure and software development practices, also
coding and database definition\\
Geoentrópica & July 2008 & Web Infrastructure, consulting on better
software developing practices\\
Colserauto & Septiembre 2007 - Enero 2008 & Vinapp Design, coding 
and implementation:  VIN verification, generation and identification.\\
Critical Cargo's Enterprise & July 2007 - May 2008 & Cargotrace Design,
coding an implementation de CargoTrace: Call Center vehicle georeferenced
Tracing System in Colombia and Ecuador.\\
Colegio Bethlemitas Bogotá & Diciembre 2007-Enero 2008 & Web Server
Migration to Own Machine, virtual education services, email for 1500
users, firewall and proxy\\
Centro de Comunicación Social & junio-2007 & Asesoramiento migración a
Software Libre, montaje de listas de correo y servicios web \\
Servicio Apostólico Latinoamericano & julio-agosto 2007 & Asesoramiento migración a
Software Libre, montaje de servicios de correo electrónico y servicios
web\\
Centro de Comunicación Social & 2007 & Free software migration Consulting\\
Servicio Apostólico Latinoamericano & 2007 & Free software migration Consulting\\
Colegio Saulo de Tarso & 2007 & Migration to GNU/Linux \\
Colegio Oblatas al Divino Amor & 2006 & Migration to GNU/Linux \\
CorporaciÓn Reiniciar & 2006 & Migration to GNU/Linux \\
Software House & 2006 & Websafi Consulting and extension \\
Geoentropica & 2006 & Consulting on system information for IDEAM and FAC \\
Fundación Universitaria San Martín & 2001-2003 & Sirio
Lab. Director(Research and development) \\
Eclipse Flowers & 2000 & Planning, Design and development of GFPP(Free
software for flower production prediction)\\
Gimnasio Fidel Cano & 1998-2008 & Design, teaching, implementation of the
project GNU/Linux in Colombian schools , on Primary, high school,
teachers and administrative staff. \\
Támara Patiño Ltda. & 1998-2001 & Project ``GNU/Linux en
Colegios Colombianos'' leader \\
Legislación e Informática & 1995-1996 & Implementation of Omnilege installer \\
\hline
\end{longtable}}

\section{Presentations, Speeches, And Talks}

Here some free software presentations, speeches and talks given.

{\center
\begin{longtable}{p{2.2cm}p{2.2cm}p{2.5cm}p{8.7cm}}
\hline
\textbf{Date} & \textbf{Event} & \textbf{Subject} & \textbf{Summary} \\
\hline
October 2008 & Congreso Internacional de Software Libre y
democratización del conocimiento & Colombian Case Studies &
Presentation of some of the uses of free software in Colombian
Education Institutions \\
June 2006 & Feria de educacion y tecnologia libre & Free material
production & Some experiences learned about the production of material
by school students. \\
October 2005 & Foro Local & Students producing materials & Show of
some products of programation and methodology to accomplish such task\\
May 2005 & UTP & SLEC presentation and  Linux at GFC & The SLEC
community was presented and also showed a successful implementation of
Linux at a school \\
October 2004 & SLUD 3 & Python in Education & I presented Python as an
appropiate language to articulate a curriculum in schools and many
courses at University \\
April 2003 & SLEC Conferences & GFC and FS & It was shown the GFC as
study case showing a school 100\% free software  \\
September 2001 & Speeches at San Martín & Free Software in
universities & It was showed to students the benefits of using free
software in their day to day\\
June 2000 & Free Software Talks & Free software at schools & It was
shown Linux as an operating system usable for schools, GFC as an example.\\
May 2000 & Foro distrital de educación  & Free Software in
schools & Ut supra \\
\endhead
\multicolumn{2}{r}{Continues}
\endfoot
\endlastfoot
\hline
\end{longtable}
}


\section{Volunteer work}
\begin{itemize}
\item Work at FLISOL(Free Software LatinAmerican Festival)
  2004-2007. Registry System.
\item Fundación Educativa y Cultural Támara Patiño. 2002-
\item Spanish translator GNU project documentation.2000-2002
\item Spanish translator Debian project documentation . 2003-
\item Cofounder and member of ``SLEC'' 2000-
\item Founder and developer of Structio project. 2000-
\item sysadmin of math's students server Universidad de los Andes asismat4  1998-1999
\end{itemize}
\end{document}

