\section{Advisory, Consulting and Freelancing}
\begin{entrylist}

  \entry
	{11/16-04/17}
	{External Consultant}
	{SIAS Colombia {\sl Insurance sector company}}
	{Design and implementation of system to reconstruct 3D vehicles accidents,
	by using drones and 3D software.}

  \entry
	{09/15-10/15}
	{External Consultant}
	{Recaudos Bogotá}
        {Consultant on development methodologies, by using Git, Continuous devel-
opment, and TDD.

	Consultant on the use of Ingenico’s XML libraries in data phones.}

  \entry
	{01/09-12/09}
	{External Consultant}
	{Colciencias {\sl State Institute for promotion of science and technology}}
        {Actuarial technique assessment component of the methodological guide for
the Colombian health system.

Consulting in actuarial process in the POS rating.

Analysis of the databases of the Ministry of Health.

Develop a sure method to give people data to keep abbeas data.

Suggestions on the working mechanism using agile methodologies, like
	Scrum.}

  \entry
	{10/09-11/09}
	{External Advisor}
	{Universidad de los Andes {\sl Department of Mathematics}}
	{Organization of the Third National Symposium of Actuary.}

  \entry
	{01/06–12/07}
	{Assistant Consultant}
	{Asesorías Actuariales {\sl Advisory and consulting company}}
	{Reserve calculation and segmentation ARP Social Security. Contingency.

Calculation for Carvajal business group. Development of the Middleware be-
tween Fortran to OpenOffice.org.

Migration of company’s software from Office to OpenOffice.

I Reviewed the calculation of pension funds for the Colombian Ministry of
	Defence.}

\end{entrylist}

