\begin{entrylist}
  \entry
    {05/23-04/24}
    {Data Engineering, Remote, Senior}
    {Sonder {\sl Protect Company}}
    {Engineered a custom SQLFluff \href{http:\\https://github.com/juanfejara/sqlfluff-templ-check}{plugin}
    to enforce the standardized use of DBT ref() syntax across SQL codebases, improving data model consistency
    and lineage tracking. Led the migration from a legacy DBT ETL system to a domain-driven, medallion-architected
    DBT project on Snowflake, maintaining a seamless backward compatibility layer to ensure uninterrupted
    business operations during transition.}
  \entry
    {05/21-05/23}
    {Data Engineering, Remote, Senior}
    {Ebury {\sl exchange Fintech}}
    {Ebury is a Fintech based in London and Malaga, belonging to the Santander group, which exchanges
foreign exchange, and has a presence in 24 countries.
    Spearheaded the migration of a monolithic Django ORM back-office system to a modern BigQuery data
    warehouse using dbt and Airflow, enhancing scalability and data centralization. Optimized
    critical reports and ETL pipelines through performant Python, Bash, and SQL scripts, deploying
    solutions via Docker containers on Kubernetes and distributed task queues with Celery. Engineered and
    maintained a hybrid cloud infrastructure spanning AWS and GCP to support robust, scalable data operations.}
  \entry
    {03/20-12/22}
    {Python Developer, Data Science, Senior}
    {Globant {\sl Software development company}}
    {SmileBuilder and SmileTreatment; Developed orthodontic treatment planning software, applying differential
    geometry principles to accurately model and reproduce patient jaws in 3D. Drove efficiency within Johnson \&
    Johnson's Data Science team by architecting and implementing Python plugins for Dataiku DSS, expanding
    platform capabilities and promoting maintainable code practices.}
  \entry
    {01/16-11/19}
    {Data Science, Fullstack Programmer}
    {OpDevel {\sl Consultant and dev. company}}
    {Fraud Prevention \textbf{Tpaga}, reduction of fraud in 7\% in the Walled App, by creating an innovative new methodology. Data Processing, \textbf{Python} Developer. \textbf{Crossover.com} Remote work company.

Consultant Developer. Certicamara, certification company. Java8, under DropWizard as backend and NodeJS as frontend NodeJS REST architecture, using Mongo, RabbitMQ, and helping in using AWS and GCP by Kubernetes and Dockers. Data Scientist. Civico App. Data analysis, I introduced data analysis by using innovative physics software as ROOT and Jupyter, producing a big impact in
the company.

I built a scrapper to consult medicines on web pages, to Assisprex’s call center. Voice recognition system, using CUDA to phone call transcription in call center at Assisprex company.

Project Manager. Tracking and video streaming system for vehicle. Consultant. Video capturing system and 3D scene reconstruction of vehicle accidents.

Conceptual Design of IT infrastructure budget in Toll concession Honda - Girardot. Caracol transport software in Haiti. Ingenico developer for Transmilenio card system, consultant to Recaudo Bogotá. For the company GSD+.}

  \entry
	{02/13-12/15}
	{P. Owner, P. Manager, Senior programmer}
	{Brückner {\sl German Plastic Machine builder company}}
	{PEM process program, for customers. Develop a model to improve the pro-
cess of our customers.

	Development of a MRP, based on Odoo with application on stretching lines.}
\end{entrylist}

%\newpage

\begin{entrylist}
  \entry
	{06/10-02/13}
	{Data Scientist, Research Programmer}
	{EmQbit {\sl Technology-oriented company}}
	{Data Scientist for Risk and Fraud Detection in the project Detect TA, and DTA.
Develop Web application, under Google App Engine, for mortgage manage-
ment.

Develop of mathematical models for mortgage assignments.

Application development for the safety of voting machines using crypto-
graphic keys at booting time in Linux, by altering the Kernel at boot time.

	Application for Book Self Checking, in the National University’s library.}
  \entry
	{01/07-06/10}
	{CTO, Programmer}
	{Mig Internacional {\sl Technology-oriented company}}
	{Automatic identification systems such as radio frequency identification (RFID)
and optical character recognition (OCR), with adaptations.

Embedded camera, using FPGA to make Line Plate Recognition.

RFID equipment development in Germany, that uses FPAA to process the
	Tag signal.}

  \entry
	{06/04-12/06}
	{Casualty Actuary}
	{Allianz Colseguros S.A. {\sl Insurance Company.}}
	{Designer of the BD CEXPER, a subscription credit bureau.

Analysis of Technical Note for automobile’s vice presidential.

Organization of the Second National Symposium of Actuary.

Developer the connector between the software Tricast to the company's software.

Evaluation of software for the actuarial team, Emblem and Tricast.}

  \entry
	{12/02-01/04}
	{Statistical QC}
	{PGS Onshore {\sl Seismic Company}}
	{Analysis of statistics. Development of ERP (Pachallaqta) to manage projects
	using 3D seismic in C++ and Oracle.}

  \entry
	{01/96-12/01}
	{IT Manager, Developer}
	{Xania LTDA. {\sl Software development company}}
	{Software related to coal mining Intercor, now Cerrejón S.A.

Software for assessment of losses in motor vehicles (Palm Pilot), Company
Subocol.

Software Infoban: for the Ministry of Justice (Web - Oracle Web Server, C, C++)
ERP support and migration of the ERP core from Pascal to Delphy, and develop
of Software Edition and Educational Building Development Manager.
Educational software. Company Telemundo Editors. Using Macromedia
products “Authorware, Director”, Visual Basic, Pascal, and Borland Delphy C.

%Creation of the emulator for NDC + (protocol of NCR and Diebold ATM) for
%ATM Tryton using C++. Company RK Technologies, a company dedicated to
%the production of ATM and banking software.
%Built and programmed robot automation for the Children’s Museum in Bogotá.
%Company Microservicios

%Developing a search algorithm for DOS software and development of hypertext
%software for Windows 3.1 using Borland C++. Company Leginfo Ltda.}
}

  \end{entrylist}
