\section{Professorship}
\begin{entrylist}
  \entry
    {08/2006-05/2007}
    {Term professor}
    {Pontificia Universidad Javeriana}
    {\begin{itemize}
       \item{Professor of Programming Languages: functional and logic programming.}
       \item{Professor of Algorithm Analysis: complexity, algorithms and problem solving strategies.}
     \end{itemize}}
  \entry
    {01/2001-11/2002}
    {Research Director}
    {Fundación Universitaria San Martín}
    {My main task was devoted mainly to guide students on their
    graduation projects, guide a team to develop some of the tools
    neede by the students of the faculty and also offer some courses
    in programming area
      \begin{itemize}      
       \item{Professor of Internet Oriented Programming: Web frameworks and bare programming for the web}
       \item{Professor of Basics of Object Oriented Programming: For first semester students, they 
       started problem solving, basic algorithms and Java as a first language.}
       \item{Professor of Functional and logic programming: With Prolog, Haskell and Ocaml.}
       \item{Professor of Data Structures: As a third course in the programming line of Systems Engineering.}
     \end{itemize}}
  \entry
     {08/2000-11/2000}
     {Term professor}
     {Fundación Universitaria San Martín}
     {\begin{itemize}
        \item{Professor of Object Oriented Programming:For students that already had programming notions.}
      \end{itemize}}
  \entry
    {01/1998-05/1999}
    {Term professor}
    {Universidad de los Andes}
    {\begin{itemize}
       \item{Professor of Integral Calculus: in the programs of Engineering, Department of Maths, Faculty of Sciences.}
       \item{Professor of Differential Calculus: in the programs of Engineering, Department of Maths, Faculty of Sciences.}
     \end{itemize}}
\end{entrylist}
\begin{entrylist}
    \entry
     {1998-2008}
     {Chair professor}
     {Gimnasio Fidel Cano}
     {The students of this school are around the world, they own companies,
     have families, they have changed their world in many different areas,
     some of them are programmers, and they share their experiences and
     knowledge.  In the school they learned about free software and its principles
     had the opportunity to take the learning by themselves and are succesful
     doing many different things.  They opensourced the games they created and also
     helped doing some translations like the Emacs Tutorial to spanish, among other
     things. 
       \begin{itemize}
        \item{Professor of Programming: Python}
        \item{Professor of Programming: Python and Zope}
        \item{Professor of Programming: Java}
        \item{Professor of Programming: C and Java}
        \item{Professor of Trigonometry}
      \end{itemize}}
 \end{entrylist}
